Exploring the Relationship Between Anime Scores, Popularity, and Favorites

### 2024-12-04 paper/paper.qmd
Update paper pdf

For this analysis, the dataset was compiled using data extracted from the MyAnimeList API, which provides key variables such as anime titles, scores, popularity, and the number of list users. The "number of favorites" data, however, was not available through the API, so it was manually compiled by directly listing the values from the MyAnimeList website and included in the dataset for analysis. These data points were then cleaned and processed for analysis using the statistical programming software R [@citeR]. The analysis utilized several R packages from the tidyverse [@citeTidyverse], ggplot2 [@citeGgplot] for visualization, `rstanarm` [@rstanarm], `arrow` [@citearrow] and `knitr` [@citeKnitr]`. Data processing tasks, such as handling missing values and transforming variables, were carried out to ensure the dataset was ready for analysis.

@@

```{r}
#| label: fig-favorites-histogram
#| fig-cap: "Histogram of Popularity for Top 10 Highest-Rated Anime"
#| echo: false
#| warning: false
#| message: false

>>>>

For this analysis, the dataset was compiled using data extracted from the MyAnimeList API, which provides key variables such as anime titles, scores, popularity, and the number of list users. The "number of favorites" data, however, was not available through the API, so it was manually compiled by directly listing the values from the MyAnimeList website and included in the dataset for analysis. These data points were then cleaned and processed for analysis using the statistical programming software R [@citeR]. The analysis utilized several R packages from the tidyverse [@citeTidyverse], ggplot2 [@citeGgplot2] for visualization, `rstanarm` [@rstanarm], `arrow` [@citearrow] and `knitr` [@citeKnitr]`. Data processing tasks, such as handling missing values and transforming variables, were carried out to ensure the dataset was ready for analysis.

@@

```{r}
#| label: fig-popularity-histogram
#| fig-cap: "Histogram of Popularity for Top 10 Highest-Rated Anime"
#| echo: false
#| warning: false
#| message: false
